---
output: 
  github_document:
    html_preview: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
# Load package functions
devtools::load_all()
```

# rtdd

Bring near real-time hydrometric data from [the Government of Canada's DataMart service](https://dd.weather.gc.ca/hydrometric/) into R. 

Note that much of this funcionality is built into [`tidyhydat`](https://github.com/ropensci/tidyhydat). Use that if you can. 

## Installing
```{r eval=FALSE}
if(!requireNamespace("remotes")) install.packages("remotes")
remotes::install_github('rywhale/rtdd')
```

## Station Metadata
### All Stations
By default, `dd_hydro_meta` will return metadata for all avaiable stations, across Canada

```{r}
stn_meta <- dd_hydro_meta()
str(stn_meta)
```

### By Province/Territory
You can also filter by a province or territory short code. See `?dd_hydro_meta` for valid options

```{r}
ont_stn_meta <- dd_hydro_meta(prov_terr = "ON")
```

## Station Data
You can retrieve either an individual station's data or all the data available for given a province or territory.
There are also multiple update intervals available:

* **hourly** - (Default) Last 2 complete days of data plus the current incomplete day
* **daily** - Last 30 complete days of data plus the current incomplete day

### Single Station
```{r}
stn_data <- dd_hydro_data(station_id = "05QB002", prov_terr = "ON")
str(stn_data)
```

### All Stations in Province/Territory
You can grab all the data for a given province/territory by setting `all_stns=TRUE`. 
```{r}
all_stn_data <- dd_hydro_data(prov_terr = "YT", all_stns = TRUE)
str(all_stn_data)
```


